% References
\renewcommand{\bibname}{مراجع}
\addcontentsline{toc}{section}{مراجع}

\begin{thebibliography}{99}

\begin{latin}

\baselineskip=.7cm

\bibitem{ndn}
Van Jacobson, Diana K. Smetters, James D. Thornton, Michael F. Plass, Nicholas H. Briggs, and Rebecca L. Braynard. 2009. \textit{Networking named content}. In Proceedings of the 5th international conference on Emerging networking experiments and technologies (CoNEXT '09). ACM, New York, NY, USA, 1-12.

\bibitem{less_pain}
Seyed Kaveh Fayazbakhsh, Yin Lin, Amin Tootoonchian, Ali Ghodsi, Teemu Koponen, Bruce Maggs, K.C. Ng, Vyas Sekar, and Scott Shenker. 2013. \textit{Less pain, most of the gain: incrementally deployable ICN}. In Proceedings of the ACM SIGCOMM 2013 conference on SIGCOMM (SIGCOMM '13). ACM, New York, NY, USA, 147-158. 

\bibitem{dona}
Teemu Koponen, Mohit Chawla, Byung-Gon Chun, Andrey Ermolinskiy, Kye Hyun Kim, Scott Shenker, and Ion Stoica. 2007. \textit{A data-oriented (and beyond) network architecture}. In Proceedings of the 2007 conference on Applications, technologies, architectures, and protocols for computer communications (SIGCOMM '07). ACM, New York, NY, USA, 181-192. 

\bibitem{adaptive_web_caching}
Scott Michel, Khoi Nguyen, Adam Rosenstein, Lixia Zhang, Sally Floyd, and Van Jacobson. 1998. \textit{Adaptive web caching: towards a new global caching architecture}. Comput. Netw. ISDN Syst. 30, 22-23 (November 1998), 2169-2177


\bibitem{location_cache}
Krishnan, P.; Raz, D.; Shavitt, Y., \textit{"The cache location problem,"} in Networking, IEEE/ACM Transactions on , vol.8, no.5, pp.568-582, Oct 2000
doi: 10.1109/90.879344

\bibitem{web_caching}
Barish, G.; Obraczke, K., \textit{"World Wide Web caching: trends and techniques,"} in Communications Magazine, IEEE , vol.38, no.5, pp.178-184, May 2000

\bibitem{zipf}
Breslau, L.; Pei Cao; Li Fan; Phillips, G.; Shenker, S., \textit{"Web caching and Zipf-like distributions: evidence and implications,"} in INFOCOM '99. Eighteenth Annual Joint Conference of the IEEE Computer and Communications Societies. Proceedings. IEEE , vol.1, no., pp.126-134 vol.1, 21-25 Mar 1999

\bibitem{survey_caching}
Meng Zhang; Hongbin Luo; Hongke Zhang, \textit{"A Survey of Caching Mechanisms in Information-Centric Networking,"} in Communications Surveys \& Tutorials, IEEE , vol.17, no.3, pp.1473-1499, thirdquarter 2015

\bibitem{cl4m}
Wei Koong Chai, Diliang He, Ioannis Psaras, and George Pavlou. 2012. \textit{Cache "less for more" in information-centric networks}. In Proceedings of the 11th international IFIP TC 6 conference on Networking - Volume Part I (IFIP'12), Robert Bestak, Lukas Kencl, Li Erran Li, Joerg Widmer, and Hao Yin (Eds.), Vol. Part I. Springer-Verlag, Berlin, Heidelberg, 27-40. 

\bibitem{cache_energy}
Fang, C., Yu, F. R., Huang, T., Liu, J., \& Liu, Y. (2014). \textit{Energy-efficient distributed in-network caching for Content-Centric Networks}. Proceedings - IEEE INFOCOM (pp. 91-96)

\end{latin}


\end{thebibliography}